### 2022-08-22 docs/accepted/manuscript.Rmd
init

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  - \usepackage{tcolorbox}
  #- \pagewiselinenumbers
  - \raggedbottom

  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
---

@@

\vspace{-1.1em}
\begin{center}
\begin{tcolorbox}[colframe=blue!75!black,boxrule=0.75pt,arc=5pt,width=4in]
\centering\textcolor{blue!75!black}{In-press at \emph{Psychonomic Bulletin \& Review}}
\end{tcolorbox}
\end{center}
\vspace{0.5em}

@@

```{r table1, echo = FALSE, results = "asis"}
table1 <- tibble::tibble(
    c1 = c("Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation",
           "Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation"),
    c2 = c("0.68",
           "0.86",
           "0.86",
           "0.39",
           "0.92",
           "0.91"),
    c3 = c("0.81",
           "0.93",
           "0.90",
           "0.73",
           "0.88",
           "0.91"),
    c4 = c("0.80",
           "0.95",
           "0.92",
           "0.79",
           "0.91",
           "0.93"),
    c5 = c("0.83",
           "0.94",
           "0.93",
           "0.85",
           "0.91",
           "0.94"),
)
table1 %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      linesep = "\\addlinespace",
      caption = "Cronbach's alpha for each questionnaire at each timepoint.",
      col.names = c("Questionnaire",
                  "After pre-test",
                  "After block 1",
                  "After block 6",
                  "Before retention")
  ) %>%
  kable_styling(position = "left",
                font_size = 11,
                latex_options = "scale_down") %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "7em") %>%
  pack_rows("Experiment 1", 1, 3) %>%
  pack_rows("Experiment 2", 4, 6) %>%
  footnote(general = "Block 1 and 6 are from the acquisition phase.",
           general_title = "Note.",
           title_format = "italic",
           footnote_as_chunk = TRUE
           )
```

@@

```{r table2, echo = FALSE, results = "asis"}
table2 <- tibble::tibble(
    c1 = c("Choice+Error-Feedback",
           "Choice+Graded-Feedback",
           "Yoked+Error-Feedback",
           "Yoked+Graded-Feedback",
           "Choice+Binary-Feedback",
           "Yoked+Binary-Feedback"),
    c2 = c("4",
           "2",
           "1",
           "3",
           "2",
           "4"),
    c3 = c("0--2",
           "0--1",
           "0--1",
           "0--1",
           "0--1",
           "0--1"),
    c4 = c("30",
           "26",
           "28",
           "33",
           "14",
           "10"),
    c5 = c("0--4",
           "0--4",
           "0--3",
           "0--3",
           "0--3",
           "0--2"),
)
table2 %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      linesep = "\\addlinespace",
      caption = 'Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.',
      col.names = c("Group",
                  "Total",
                  "Min--Max",
                  "Total",
                  "Min--Max")
  ) %>%
  kable_styling(position = "left",
                font_size = 11,
                latex_options = "scale_down") %>%
  column_spec(1, width = "15em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "5em") %>%
  add_header_above(c(" ", "Spatial goal" = 2, "Timing goal" = 2)) %>%
  pack_rows("Experiment 1", 1, 4) %>%
  pack_rows("Experiment 2", 5, 6)
```

@@

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  #- \pagewiselinenumbers
  - \raggedbottom

  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
---

@@

@@

```{r table1, echo = FALSE, results = "asis"}
table1 <- tibble::tibble(
    c1 = c("Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation",
           "Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation"),
    c2 = c("0.68",
           "0.86",
           "0.86",
           "0.39",
           "0.92",
           "0.91"),
    c3 = c("0.81",
           "0.93",
           "0.90",
           "0.73",
           "0.88",
           "0.91"),
    c4 = c("0.80",
           "0.95",
           "0.92",
           "0.79",
           "0.91",
           "0.93"),
    c5 = c("0.83",
           "0.94",
           "0.93",
           "0.85",
           "0.91",
           "0.94"),
)
table1 %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      linesep = "\\addlinespace",
      caption = "Cronbach's alpha for each questionnaire at each timepoint.",
      col.names = c("Questionnaire",
                  "After pre-test",
                  "After block 1",
                  "After block 6",
                  "Before retention")
  ) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "7em") %>%
  pack_rows("Experiment 1", 1, 3) %>%
  pack_rows("Experiment 2", 4, 6) %>%
  footnote(general = "Block 1 and 6 are from the acquisition phase.",
           general_title = "Note.",
           title_format = "italic",
           footnote_as_chunk = TRUE
           )
```

@@

```{r table2, echo = FALSE, results = "asis"}
table2 <- tibble::tibble(
    c1 = c("Choice+Error-Feedback",
           "Choice+Graded-Feedback",
           "Yoked+Error-Feedback",
           "Yoked+Graded-Feedback",
           "Choice+Binary-Feedback",
           "Yoked+Binary-Feedback"),
    c2 = c("4",
           "2",
           "1",
           "3",
           "2",
           "4"),
    c3 = c("0--2",
           "0--1",
           "0--1",
           "0--1",
           "0--1",
           "0--1"),
    c4 = c("30",
           "26",
           "28",
           "33",
           "14",
           "10"),
    c5 = c("0--4",
           "0--4",
           "0--3",
           "0--3",
           "0--3",
           "0--2"),
)
table2 %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      linesep = "\\addlinespace",
      caption = 'Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.',
      col.names = c("Group",
                  "Total",
                  "Min--Max",
                  "Total",
                  "Min--Max")
  ) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  column_spec(1, width = "15em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "5em") %>%
  add_header_above(c(" ", "Spatial goal" = 2, "Timing goal" = 2)) %>%
  pack_rows("Experiment 1", 1, 4) %>%
  pack_rows("Experiment 2", 5, 6)
```

@@

\vspace{10ex}
